---
title: "MOSAIC Study Progress"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cosmo
    logo: favicon_48x48.png
    favicon: favicon_48x48.png
---

<style>                     
.navbar {
  background-color:#003D79;
  border-color:white;
}
.navbar-brand {
color:white!important;
}
</style>   

<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 15px

</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(highcharter)
library(treemap)
library(knitr)

source("datamgmt_progress.R")

mosaic_pal <- c(
  ## Row 1, starting with leftmost diamond
  "blue1" = "#283C72", "blue2" = "#243E8B", "blue3" = "#0477BF",
  "green1" = "#8EC63E", "green2" = "#3BB547",
  ## Row 2
  "blue4" = "#24ADCD", "blue5" = "#0976B7", "blue6" = "#23AEDD",
  "green3" = "#3BB54A", "green4" = "#1A653E",
  ## Row 3
  "orange1" = "#E76A32", "orange2" = "#F69723", "orange3" = "#FA961F",
  "orange4" = "#FBCD93", "ecru" = "#FFF8DE",
  ## Row 4
  "red1" = "#D71A60", "red2" = "#F27074", "red3" = "#EC835F",
  "gray1" = "#E4DAD1", "gray2" = "#F7F5EB",
  ## Row 5
  "red4" = "#C0232C", "red5" = "#EE1C27", "red6" = "#FF686D",
  "red7" = "#F8D4D1", "cream" = "#FEFEFC"
)

## Function to get hex for a specific element
mosaic_col <- function(hex){ as.character(mosaic_pal[hex]) }

## Named vector of colors for exclusions
exc_colors <- c(
  ">5 hospital days in last 30" = mosaic_col("blue1"),
  "Severe neurologic injury" = mosaic_col("blue3"),
  "Death within 24h/hospice" = mosaic_col("blue4"),
  "Rapidly resolving organ failure" = mosaic_col("blue5"),
  "BMI > 50" = mosaic_col("red1"),
  "Substance abuse, etc" = mosaic_col("red2"),
  "Blind, deaf, English" = mosaic_col("red3"),
  "Prisoner" = mosaic_col("red4"),
  "Inability to live independently" = mosaic_col("red5"),
  "Homeless" = mosaic_col("red6"),
  "Patient/surrogate refusal" = mosaic_col("green4"),
  "No surrogate within 72h" = mosaic_col("green1"),
  "Attending refusal" = mosaic_col("green3"),
  ">72h eligibility prior to screening" = mosaic_col("green4"),
  "Lives >150 miles from VUMC" = mosaic_col("orange1"),
  "Study with no co-enrollment" = mosaic_col("orange2"),
  "Other" = mosaic_col("orange3")
)

## Manually set width, height for screening/enrollment over time plots
screenplot_wd <- 640
screenplot_ht <- 325

```

Screening & Enrollment
=====================================

Column {data-width=700}
-----------------------------------------------------------------------

### Patients Screened, Approached, and Enrolled

```{r nodate_ids}
nodate_ids <- unique(c(exc_id_nodate, enroll_id_nodate))

nodate_statement <- ifelse(
  length(nodate_ids > 0),
  paste(
    "These IDs have no exclusion/enrollment date entered and are not included:",
    paste(nodate_ids, collapse = "; ")
  ),
  ""
)

```

`r nodate_statement`

```{r screening}
## Want figure to start in March 2017
screening_myears <- unique(screening_summary$myear)
screening_myears_num <- 1:length(screening_myears)
names(screening_myears_num) <- screening_myears

screening_summary <- screening_summary %>%
  mutate(myear_num = screening_myears_num[myear])

x_screen <- list(tickvals = as.numeric(screening_myears_num),
                 ticktext = unique(screening_summary$myear_char),
                 title = "")
y <- list(title = "")

screen_plotly <- plot_ly(
  data = screening_summary,
  x = ~ myear_num,
  y = ~ Screened,
  type = "bar",
  name = "Screened",
  color = I(mosaic_col("red5")),
  alpha = 0.75
) %>%
  add_bars(
    y = ~ Approached,
    name = "Approached",
    color = I(mosaic_col("orange3"))
  ) %>%
  add_bars(
    y = ~ Enrolled,
    name = "Enrolled",
    color = I(mosaic_col("green4"))
  )

screen_plotly %>%
  layout(legend = list(x = 0, y = 0.95, bgcolor='transparent'),
         xaxis = x_screen, yaxis = y)

```

### Study Exclusions (% of All Patients Excluded)

```{r exclusions_over_time}
## plotly needs x value to be numeric to sort properly?
exc_myears <- sort(unique(exc_over_time$myear))
exc_myears_num <- 1:length(exc_myears)
names(exc_myears_num) <- exc_myears

exc_over_time <- exc_over_time %>%
  mutate(myear_num = exc_myears_num[myear])

x_exc <- list(tickvals = as.numeric(exc_myears_num),
              ticktext = unique(exc_over_time$myear_char),
              title = "")
y_exc <- list(tickvals = seq(0, 100, 20),
              ticktext = paste0(seq(0, 100, 20), "%"),
              title = "Percent of Exclusions")

exc_plotly <- plot_ly(
  data = exc_over_time,
  x = ~ myear_num,
  y = ~ Percent,
  type = "scatter",
  mode = "lines+markers",
  color = ~ Reason,
  colors = exc_colors,
  alpha = 0.6
)

exc_plotly %>%
  layout(showlegend = FALSE,
         xaxis = x_exc,
         yaxis = y_exc)

```

Column {data-width=300}
-----------------------------------------------------------------------

### Cumulative Enrollment as of `r format(Sys.Date(), "%B %d, %Y")` {data-height=250}

```{r enrollment}
screening_statement <- sprintf(
  "We have screened %s patients; %s%% were excluded and %s%% approached. Of those approached, %s%% refused consent and %s%% were enrolled.",
  n_screened,
  round(pct_excluded*100),
  round(pct_approached*100),
  round(pct_refused*100),
  round(pct_enrolled*100)
)

enroll_gauge <- gauge(
  value = n_enrolled,
  min = 0,
  max = n_goal,
  sectors = gaugeSectors(colors = mosaic_col("green1")),
  label = "patients"
)

enroll_gauge

```

### Approach & Refusal {data-height=250}

`r screening_statement`

### Cumulative Exclusions (Total: `r nrow(exc_df)`) {data-height=500}

```{r exclusions_cumulative}
tm_exc <- treemap(dtf = exc_cumul,
                  index = c("reason_type", "Reason"),
                  vSize = "n_reason",
                  type = "index",
                  title = "",
                  algorithm = "squarified",
                  palette = mosaic_pal[c("orange1", "green2", "blue3", "green4", "red1")],
                  draw = FALSE)

hc_tm_exc <- hctreemap(
  tm_exc,
  allowDrillToNode = TRUE,
  layoutAlgorithm = "squarified",
  levels = list(levelIsConstant = "false"),
  dataLabels = list(style = list(color = "white",
                                 textOutline = "0px contrast",
                                 fontSize = "8px"))
)

hc_tm_exc

```

In-Hospital
=====================================

Column {data-width=500}
-----------------------------------------------------------------------

### Pre-Hospital Questionnaires {data-height=40}

### Prehospital Surrogate Battery Completion Rate

```{r ph_comp}
pct_surrogate_comp <-
  round(mean(all_enrolled$ph_surrogate_comp, na.rm = TRUE) * 100)
pct_caregiver_comp <-
  round(mean(all_enrolled$ph_caregiver_comp, na.rm = TRUE) * 100)

```

```{r ph_surrogate}
valueBox(
  value = paste0(pct_surrogate_comp, "%"),
  caption = "fully completed surrogate questionnaires<br>(General, PASE, ADLs, LS, employment, AUDIT, IQCODE)",
  color = ifelse(pct_surrogate_comp < 80, mosaic_col("orange3"), mosaic_col("green3")),
  icon = "ion-person-stalker"
)

```

### Prehospital Caregiver Battery Completion Rate

```{r ph_caregiver}
valueBox(
  value = paste0(pct_caregiver_comp, "%"),
  caption = "fully completed caregiver questionnaires<br>(Zarit, Memory & Behavior)",
  color = ifelse(pct_caregiver_comp < 80, mosaic_col("orange3"), mosaic_col("green3")),
  icon = "ion-heart"
)

```

### Specimen Log Compliance at Discharge (% of Patients)

```{r specimen_compliance}
specimen_plot <- ggplot(data = specimen_rsns,
                        aes(group = Color, x = Reason, y = Percent)) +
  geom_bar(aes(alpha = (Reason == "Compliant"), fill = Color),
           position = "dodge", stat = "identity") +
  scale_y_continuous(limits = c(0, 100),
                     breaks = seq(0, 100, 50),
                     labels = paste0(seq(0, 100, 50), "%")) +
  scale_fill_manual(values = c(mosaic_col("blue3"), "#5F0395"), guide = FALSE) +
  scale_alpha_manual(values = c(0.65, 0.85)) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text = element_text(size = 10),
        panel.background = element_rect(fill = NA, color = "gray80"),
        panel.spacing = unit(2, "lines"))

x <- y <- list(title = NULL)

specimen_plot %>%
  ggplotly(tooltip = c("x", "y", "group")) %>%
  layout(xaxis = x, yaxis = y)

```

### Current In-Hospital Status

```{r current_status}
## List of patients currently in hospital
pts_inhosp <- subset(all_enrolled, inhosp_status == "Still in hospital")$id
pts_inhosp_text <- ifelse(length(pts_inhosp) == 0, "None",
                          paste0(pts_inhosp, collapse = "; "))

tm_status <- treemap(
  dtf = status_count,
  index = c("inhosp_status"),
  vSize = "n_status",
  type = "index",
  title = "",
  algorithm = "squarified",
  palette = mosaic_pal[c("blue3", "red1", "orange1", "green2")],
  draw = FALSE
)

hc_tm_status <- hctreemap(
  tm_status,
  allowDrillToNode = TRUE,
  layoutAlgorithm = "squarified",
  levels = list(levelIsConstant = "false"),
  dataLabels = list(style = list(color = "white",
                                 textOutline = "0px contrast",
                                 fontSize = "12px"))
) %>%
  hc_subtitle(
    text = paste("Patients currently in hospital:", pts_inhosp_text),
    align = "left"
  )

hc_tm_status

```

Column {data-width=500}
-----------------------------------------------------------------------
### **Accelerometer Central** {data-height=40}

### Accelerometer Snapshot: Patient-Days

```{r accel_snapshot_days}
## -- Patient-days accelerometer was removed for any reason --------------------
pct_accel_rm <- round((n_accel_rm / n_accel_days) * 100)
days_no_accel <- n_hosp_days - n_accel_days

accel_text <- ifelse(
  days_no_accel == 0,
  "days accelerometer removed >=1 time<br> <br> ",
  paste0(
    "days accelerometer removed >=1 time<br><br><b>Note</b>: ",
    days_no_accel, " days had no accelerometer data entered."
  )
)

valueBox(
  value = paste0(pct_accel_rm, "%"),
  caption = accel_text,
  color = mosaic_col("orange2"),
  icon = "fa-times"
)

```

### Accelerometer Snapshot: Patients

```{r accel_snapshot_pts}

## -- Patients for whom accelerometer was permanently removed ------------------------
pct_accel_permrm <- round((n_accel_permrm / n_enrolled) * 100)

valueBox(
  value = paste0(pct_accel_permrm, "%"),
  caption = "patients with accelerometer permanently removed<br> <br> ",
  color = mosaic_col("red4"),
  icon = "fa-times-circle"
)

```

### On Days Accelerometer Was Removed, How Many Times?

```{r times_accel_removed}
accel_rm_atleast1 <- accel_rm_df %>%
  filter(bed_device_num > 0) %>%
  rename(Times = bed_device_num)

accel_rm_hist <- ggplot(data = accel_rm_atleast1, aes(x = Times)) +
  geom_histogram(fill = mosaic_col("blue1"), alpha = 0.5, binwidth = 1) +
  scale_x_continuous(breaks = 1:8, labels = 1:8) +
  theme_minimal() +
  theme(axis.title = element_blank())

accel_rm_hist %>%
  ggplotly(tooltip = c("x", "y"))

```

### Reasons for Accelerometer Removal

```{r reasons_removed}
sum_accel_rm %>%
  knitr::kable(
    format = "markdown",
    row.names = FALSE, col.names = c("Reason", "Patients")
  )

```

Follow-Up
=====================================

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

Study & Technical Info
=====================================

MOSAIC is funded by the National Institutes of Health. Please see our listing on [clinicaltrials.gov](https://clinicaltrials.gov/ct2/show/NCT03115840).

This dashboard uses R version `r devtools::session_info()$platform$version`. Packages:

```{r}
DT::datatable(devtools::session_info()$packages)

```